VOCC outline

### 2020-04-07 ms/ms.Rmd
add list of proposed figs to ms and link to early draft figs

@@

```{r climate-maps, fig.cap="Caption goes here", out.width="5in"}
include_graphics(here("ms", "figs", "example.pdf"))
```

@@

```{r another, fig.cap="Caption goes here", out.width="5in"}
include_graphics(here("ms", "figs", "example.pdf"))
```

@@

>>>>

<!-- TODO: figures to consider
-   temperature and O2 maps and velocities; 4 panel
-   coefficient plots temp + O2; add meta-analytical coefficients?
-   some example temperature maps plus chopsticks
-   some example O2 maps plus chopsticks
-   plot coefficients against depth etc.... adults and immature separately?
-->

@@

```{r climate-maps, fig.cap="Caption goes here", out.width="6in"}
include_graphics(here("ms", "figs", "climate-maps.pdf"))
```

@@

```{r worm-plots, fig.cap="Caption goes here", out.width="8in"}
# include_graphics(here("ms", "figs", "worm-plots.pdf"))
```

```{r temp-chops, fig.cap="Caption goes here", out.width="8in"}
# include_graphics(here("ms", "figs", "temp-chops.pdf"))
```

```{r do-chops, fig.cap="Caption goes here", out.width="8in"}
include_graphics(here("ms", "figs", "do-chops.pdf"))
```

@@

Supplemental figures:
(In no particular order)
-   flow diagram
-   spatial residuals
-   null model stuff
-   all the chopstick panels
-   other coefs plot
-   velocity versions
-   pairs plot of predictors
-   plot vocc regression residuals against the main predictors... (and not in model and fitted vs. residuals plot; but don't necessarily include in paper)
